---
title: 'Graph 4: Radar'
author: ''
date: '2018-06-13'
slug: graph-3-tba
categories: []
tags: []
description: Desc
hacker_news_id: ''
lobsters_id: ''
meta_img: /images/image.jpg 
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse) 
library(ggplot2)
#library(ggalt)
library(ggradar)
library(extrafont)
library(ggfortify)
library(infer)
library(forcats)
library(ggridges)
library(here)
library(scales)
```

## Preliminaries
### Data

All the graphs of this series are generated from data concerning frequency with which words from assorted dictionaries appear in original reddit posts from various subreddits. This graph shows clusters centers generated by running K means clustering (K=7) on the data shown in `alldicts` in [graph 2](/post/2018-06-11-graph-2-raincloud/), after reducing its dimensionality through prinicipal component analyis to the 21 dimensions shown in [graph 3](/post/graph-3-tba/)
```{r}
clusters <- read_csv(here('static','data','redditProject','centers')) 

clusters
```


### Audience
In its current form, audience for this project is almost entirely myself and the professors I'm trying to convince to help me with this project. Eventually I hope to research may be of interest to a larger group, including: 

1. Linguists interested in this method of textual analysis and the language of internet forums
1. Computer sciencists interested in the distributed computing or machine learning that went into this project
1. Social scientists studying any of the many social groups involved on reddit. 


## Plot Type: Radar

### How to read it and what to look for 
The radar chart has multiple axes in a radial format. It allows visualization of high dimensional data through the use of polar coordinates. The chart includes n evenly spaced lines radiating out from the center of a circle where n is the number of dimensions to be shown on the chart. This chart is less effective for communicating exact values than something like the bar chart, but seems to be one of the best options for representing points in high dimensional space. 

### Presentation Tips
This is not a common graph, and it's important to not interpret the area of the chart as its major component. Explaining each of the axes and what they mean is important, and this graph should only be used for high level comparisions between overall shapes of the data, rather than fine grained differences in values. 

### Variations and Alternatives
This graph doesn't convey numerical values information in a very straightforward way, so it's used here as a sort of a last resort for high dimensional data. For a more reasonable number of features a grouped bar chart might be able to better communicate differences in points across features. 

## Plot Description

### Representaton 

The create these graphs, I've first clasified subreddits into 7 groups using Kmeans clustering, and then plotted the resulting cluster centers the PCA space with one principle component on each axis of the radar chart. Because the principal components can be challenging to interpret, I've labeled each of the dimensions with an approximation of what dictionaries they correlate to. 

The actual values used to plot points along these dimensions are largely arbitrary. Not only are the clusters generated based on the normalized frequency values, the values within these clusters have been normalized once again so that the smallest point each dimension is at the center of the radar plot, and the largest is on the outer circle to best express the difference between clusters. 

```{r echo=TRUE}
clusters <- clusters %>%  
  mutate_at(vars(starts_with('d')),rescale)
```

As such I've removed all the numerical labels from these points and only left the line at 50% radius for reference. 

### Methods

Most of the code below is aesthetic. I was unable to factor ggradar, so code for every plot is repeated. The most challenging part of this plot was getting all the labels to fit, for which setting `fig.height` and width in the chunk settings and `plot.extent.x.sf = 2` was essential.  

```{r, fig.height=7, fig.width=10, echo=TRUE}
radar_colour=rep(c("#FF5A5F", "#FFB400", "#007A87",  "#8CE071", "#7B0051", 
                       "#00D1C1", "#FFAA91", "#B4A76C", "#9CA299", "#565A5C", "#00A04B", "#E54C20"), 100)

 
dlabels= c('d1 ~negative', 'd2 ~bio', 'd3 ~feelings', 'd4 ~social, not feelings', 
           'd5 ~pos emote, no functional','d6 ~physics and bio','d7 ~sensing',
           'd8 ~leisure not money', 'd9 ~swearing and money, no bio',
           'd10 ~certain absolutist',
           'd11 ~work, num, no sensing',
           'd12 ~inhibition, sex, no money',
           'd13 ~home, hearing',
           'd14 ~work, acheive, no swearing',
           'd15 ~2nd person, no friends',
           'd16 ~cause, acheive, no death',
           'd17 ~friends',
           'd18 ~family',
           'd19 ~ingest',
           'd20 ~2nd person, num',
           'd21 ~home, death, no religion'
           )

ggradar(clusters[1,], grid.label.size = 0,
        plot.extent.x.sf = 2,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour)+ 
  ggtitle("point1")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 

```
```{r}
ggradar(clusters[2,], grid.label.size = 0,
        plot.extent.x.sf = 2,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[2])+
  ggtitle("point2")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 

ggradar(clusters[3,],grid.label.size = 0,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[3])+
  ggtitle("point3")+ 
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[4,], grid.label.size = 0,
        group.point.size = 3,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[4])+
  ggtitle("point4")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[5,], grid.label.size = 0,
        group.point.size = 3,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[5])+
  ggtitle("point5")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 

          
          
ggradar(clusters[6,], grid.label.size = 0,
        group.point.size = 4,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 9, 
        group.colours = radar_colour[6])+
  ggtitle("point6")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[7,], grid.label.size = 0,
        group.point.size = 4,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 9,
        group.colours = radar_colour[7])+
  ggtitle("point7")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


radar <- ggradar(clusters, 
                 font.radar = 'Lato', 
                 grid.label.size = 0,
                 group.point.size = 3,
                 axis.label.size = 3,
                 axis.labels = dlabels,
                 legend.text.size = 6,
                 plot.extent.x.sf = 2
                 )+
  ggtitle("7 cluster centers in 11 dimensions")+
  theme(legend.position="right") + 
  theme(text=element_text(family='Lato'))


radar
```
